---
title: "capstone_markdown"
author: "Jake Daniels"
date: "July 9, 2018"
output: html_document
---
# Part 2
Cleaning & Visual Packages Required
```{r, echo=FALSE}
#install.packages("tidyverse")
#install.packages("gmodels")
#install.packages("plotly")
#install.packages("reshape2")
library(tidyverse)
library(gmodels)
library(plotly)
library(reshape2)
```
## Load tele.csv manually if you skipped the AWS setup from part 1, insert your own directory where "ryersoncapstone1" is
```{r}
library(readr)
# tele_clean <- read_csv("~/ryersoncapstone1/2) Data Prep & Clean/tele.csv")
# View(tele_clean)
```

Univariate Cleaning NA/OUTLIER for Models

Billing

Class Types and Structure
```{r}
glimpse(Billing)
```

%NA
```{r}
sapply(Billing, function(x) round((sum(is.na(x))/length(x)*100),3))
```
Visualizing
```{r}
melt(Billing) %>%
  ggplot(aes(x = value)) + 
  stat_density() + 
  facet_wrap(~variable, scales = "free") +
  theme_bw()

Billing %>%
ggplot() +
geom_bar(aes(x=creditcd)) +
  theme_bw()
```
```{r}
summary(tele_clean[,2:13])
```
rev_Mean - datovr_Mean 
```{r}
# chose to drop these rows since same customers missing 5+ variables [,2:6] of numeric info
head(Billing[which(is.na(tele_clean[,2:13]$rev_Mean)),])
na_index <- which(is.na(tele_clean[,2:13]$rev_Mean))
tele_clean <- tele_clean[-na_index,]
```
change_rev
```{r}
# had more instances of NA - opting to drop
na_index <- which(is.na(tele_clean$change_rev))
tele_clean <- tele_clean[-na_index,]
```
avg6rev
```{r}
# we should have this data, opting to put median value in to keep customers to avoid extreme value's impact on mean
na_index <- which(is.na(tele_clean$avg6rev))
tele_clean[na_index,]$avg6rev <- median(tele_clean$avg6rev, na.rm = T)
```
creditcd
```{r}
# converting NA into N (no) and factor making Y/N into 1/0 factor
na_index <- which(is.na(tele_clean$creditcd))
tele_clean[na_index,]$creditcd <- "N"
tele_clean$creditcd <- ifelse(tele_clean$creditcd == "Y", 1, 0) %>% as.factor()
```

 Extreme Values
```{r}
# highlighting the extreme values then dropping them 
plot(tele_clean$rev_Mean)
plot(tele_clean$datovr_Mean)
plot(tele_clean$change_rev)

#outlier_index <- which(tele_clean$rev_Mean > 3000)
#tele_clean <- tele_clean[-outlier_index,]

#outlier_index <- which(tele_clean$datovr_Mean > 200)
#tele_clean <- tele_clean[-outlier_index,]

#outlier_index <- which(tele_clean$change_rev > 2000)
#tele_clean <- tele_clean[-outlier_index,]
```
Customer

Class Types and Structure
```{r}
glimpse(Customer)
```

%NA
```{r}
sapply(Customer, function(x) round((sum(is.na(x))/length(x)*100),3))
```
Visualizing
```{r}
melt(Customer) %>%
  ggplot(aes(x = value)) + 
  stat_density() + 
  facet_wrap(~variable, scales = "free") +
  theme_bw()
```
```{r}
summary(tele_clean[,14:42])
```
churn
```{r}
# making into a nominal value, 0 is STAYED 1 is CHURNED
tele_clean$churn <- as.factor(tele_clean$churn)
```
asl_flag
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=asl_flag)) +
  theme_bw()

# convert to 1,0 factor
tele_clean$asl_flag <- ifelse(tele_clean$asl_flag == "Y", 1, 0) %>% as.factor()
```
prizm_social_one
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=prizm_social_one)) +
  theme_bw()

# clarifying the text and setting NA to unknown
tele_clean[which(tele_clean$prizm_social_one == "S"),]$prizm_social_one <- "Suburban"
tele_clean[which(tele_clean$prizm_social_one == "U"),]$prizm_social_one <- "Urban"
tele_clean[which(tele_clean$prizm_social_one == "T"),]$prizm_social_one <- "Town & Country"
tele_clean[which(tele_clean$prizm_social_one == "C"),]$prizm_social_one <- "City"
tele_clean[which(tele_clean$prizm_social_one == "R"),]$prizm_social_one <- "Rural"
tele_clean[which(is.na(tele_clean$prizm_social_one)),]$prizm_social_one <- "UNKWN"

tele_clean$prizm_social_one <- as.factor(tele_clean$prizm_social_one)
```
area
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$area)) +
  theme_bw()  

# good for subsetting reports but not for the model, dropping this column
tele_clean$area <- NULL
```
phones/models
```{r}
# only one NA, same customer - dropping
which(is.na(tele_clean$phones)) == which(is.na(tele_clean$models))
  na_index <- which(is.na(tele_clean$phones))
  tele_clean <- tele_clean[-na_index,]
```
crdlscod
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=crdlscod)) +
  theme_bw()

# dropping full column because it has 30+ unique values and is useless for models/reports without any translation
tele_clean$crdlscod <- NULL
```
truck/rv
```{r}
# same customerinformation missing in both columns, assume they do not have - assigning 0 and factoring into Y/N
sum(which(is.na(tele_clean$truck))) == sum(which(is.na(tele_clean$rv)))
  tele_clean[which(is.na(tele_clean$truck)),]$truck <- 0 
  tele_clean$truck<- tele_clean$truck %>% as.factor()
  
  tele_clean[which(is.na(tele_clean$rv)),]$rv <- 0 
  tele_clean$rv <- tele_clean$rv %>% as.factor()
```
own_rent
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$own_rent)) +
  theme_bw()

# provides little insight and 1/3rd missing
tele_clean$own_rent <- NULL
```
lor (length of residence in years)
```{r}
# assigning the median - KNN would be great here
  na_index <- which(is.na(tele_clean$lor))
  tele_clean[na_index,]$lor <- median(tele_clean$lor, na.rm = T)
```
adults
```{r}
# keep the na by binning the data - anyone with 3-6 adults are combined into one 
tele_clean$adults <- cut(tele_clean$adults, c(0,1,2,6), labels = c("One", "Two","Three+"))
  levels(tele_clean$adults) <- c(levels(tele_clean$adults), "UNKWN")
  na_index <- which(is.na(tele_clean$adults))
  tele_clean[na_index,]$adults <- "UNKWN"
tele_clean$adults <- as.factor(tele_clean$adults)
```
dwlltype
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$dwlltype)) +
  theme_bw()

# creating UNKWN column for NA 
na_index <- which(is.na(tele_clean$dwlltype))
tele_clean[na_index,]$dwlltype <- "UNKWN"
tele_clean$dwlltype <- as.factor(tele_clean$dwlltype)
```
marital
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$marital)) +
  theme_bw()

# already an UNKNOWN column going to give NA that value
na_index <- which(is.na(tele_clean$marital))
tele_clean[na_index,]$marital <- "U"
tele_clean$marital <- as.factor(tele_clean$marital)
```
infobase
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$infobase)) +
  theme_bw()

# two resutls: one option only has 221 inputs the rest are NA values - dropping the variable
tele_clean$infobase <- NULL
```
income (estimated)
```{r}
# convert to Low (1-3), Medium(4-6), High(7-9) - putting NA into Medium(avg)
tele_clean$income <- cut(tele_clean$income, c(0,3,6,9), labels = c("Low", "Medium","High"))
  na_index <- which(is.na(tele_clean$income))
  tele_clean[na_index,]$income <- "Medium"
tele_clean$income <- as.factor(tele_clean$income)
```
numbcars
```{r}
#  NAs: 48854, half data is missing, NA likely means 0 cars, column is poorly kept so I am dropping it.
tele_clean$numbcars <- NULL
```
HHStatin
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$HHStatin)) +
  theme_bw()

# creating U column and making into factor
na_index <- which(is.na(tele_clean$HHStatin))
tele_clean[na_index,]$HHStatin <- "U"
tele_clean$HHStatin <- as.factor(tele_clean$HHStatin)
```
dwllsize
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$dwllsize)) +
  theme_bw()

# data is scarce and lacks variation, going to drop variable
tele_clean$dwllsize <- NULL
```
forgntvl
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$forgntvl)) +
  theme_bw()
# let's assume if we dont know forgntvl it is 0 since a majority is 0 already
na_index <- which(is.na(tele_clean$forgntvl))
tele_clean[na_index,]$forgntvl <- 0
tele_clean$forgntvl<- as.factor(tele_clean$forgntvl)
```
ethnic (Ethnicity roll-up code)
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=ethnic)) +
  theme_bw()

# combining all samller options into Other
na_index <- which(is.na(tele_clean$ethnic))
tele_clean[na_index,]$ethnic <- "Other"

tele_clean[which(tele_clean$ethnic != "G" & 
        tele_clean$ethnic != "H" & 
        tele_clean$ethnic != "N" & 
        tele_clean$ethnic != "S" & 
        tele_clean$ethnic != "U"),]$ethnic <- "Other"

tele_clean$ethnic <- as.factor(tele_clean$ethnic)
```
kids 0 -17
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$kid0_2)) +
  theme_bw()

#  U is unknown, Y is Yes so setting all to unknown then converting into factor
na_index <- which(is.na(tele_clean$kid0_2))
tele_clean[na_index,c("kid0_2", "kid3_5", "kid6_10", "kid11_15", "kid16_17" )] <- "U"
# making into factor
tele_clean$kid0_2 <- ifelse(tele_clean$kid0_2 == "Y", 1, 0) %>% as.factor()
tele_clean$kid3_5 <- ifelse(tele_clean$kid3_5 == "Y", 1, 0) %>% as.factor()
tele_clean$kid6_10 <- ifelse(tele_clean$kid6_10 == "Y", 1, 0) %>% as.factor()
tele_clean$kid11_15 <- ifelse(tele_clean$kid11_15 == "Y", 1, 0) %>% as.factor()
tele_clean$kid16_17 <- ifelse(tele_clean$kid16_17 == "Y", 1, 0) %>% as.factor()
```
Extreme Values
```{r}
# highlighting the extreme values then dropping them 
plot(tele_clean$uniqsubs)
plot(tele_clean$actvsubs)

#outlier_index <- which(tele_clean$uniqsubs > 100)
#tele_clean <- tele_clean[-outlier_index,]
```
CustService

Class Types and Structure
```{r}
glimpse(CustService)
```
%NA
```{r}
sapply(CustService, function(x) round((sum(is.na(x))/length(x)*100),3))
```
Visualizing
```{r}
melt(CustService) %>%
  ggplot(aes(x = value)) + 
  stat_density() + 
  facet_wrap(~variable, scales = "free") +
  theme_bw()
```

```{r}
summary(tele_clean[,38:40])
```

```{r}
# Extreme Values
plot(tele_clean$custcare_Mean)
plot(tele_clean$ccrndmou_Mean)
plot(tele_clean$cc_mou_Mean)

#outlier_index <- which(tele_clean$custcare_Mean >300)
#tele_clean <- tele_clean[-outlier_index,]

#outlier_index <- which(tele_clean$ccrndmou_Mean > 400)
#tele_clean <- tele_clean[-outlier_index,]

#outlier_index <- which(tele_clean$cc_mou_Mean > 300)
#tele_clean <- tele_clean[-outlier_index,]
```

Operations 

Class Types and Structure
```{r}
glimpse(Operations)
```
%NA
```{r}
sapply(Operations, function(x) round((sum(is.na(x))/length(x)*100),3))
```
Visualizing part 1
```{r}
melt(Operations[,2:17]) %>%
  ggplot(aes(x = value)) + 
  stat_density() + 
  facet_wrap(~variable, scales = "free") +
  theme_bw()
```
Visualizing part 2
```{r}
melt(Operations[,18:37]) %>%
  ggplot(aes(x = value)) + 
  stat_density() + 
  facet_wrap(~variable, scales = "free") +
  theme_bw()
```

```{r}
summary(tele_clean[,41:76])
```
avg6mou and avg6qty
```{r}
# we should have this data, opting to put median value in to keep customers to avoid extreme value's impact via mean
na_index <- which(is.na(tele_clean$avg6mou))
tele_clean[na_index,]$avg6mou <- median(tele_clean$avg6mou, na.rm = T)

na_index <- which(is.na(tele_clean$avg6qty))
tele_clean[na_index,]$avg6qty <- median(tele_clean$avg6qty, na.rm = T)
```

Extreme Values
```{r}
plot(tele_clean$da_Mean)
plot(tele_clean$mou_peak_data_Mean)

#outlier_index <- which(tele_clean$da_Mean > 100)
#tele_clean <- tele_clean[-outlier_index,]

#outlier_index <- which(tele_clean$mou_peak_data_Mean > 600)
#tele_clean <- tele_clean[-outlier_index,]
```


Product

Class Types and Structure
```{r}
glimpse(Product)
```
%NA
```{r}
sapply(Product, function(x) round((sum(is.na(x))/length(x)*100),3))
```
```{r}
summary(Product)
```
new_cell
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$new_cell)) +
  theme_bw()

# factoring
tele_clean$new_cell <- tele_clean$new_cell %>% as.factor()
```
dualband
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$dualband)) +
  theme_bw()

# factoring
tele_clean$dualband <- tele_clean$dualband %>% as.factor()
```
refurb_new
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$refurb_new)) +
  theme_bw()

# factoring
tele_clean$refurb_new <- tele_clean$refurb_new %>% as.factor()
```
hnd_price
```{r}
# will insert median value
na_index <- which(is.na(tele_clean$hnd_price))
tele_clean[na_index,]$hnd_price <- median(tele_clean$hnd_price, na.rm = T)
```
hnd_webcap
```{r}
tele_clean %>%
ggplot() +
geom_bar(aes(x=tele_clean$hnd_webcap)) +
  theme_bw()

# already a unwk column, moving NA to it
tele_clean[which(is.na(tele_clean$hnd_webcap)),]$hnd_webcap <- "UNKW"
tele_clean$hnd_webcap <- tele_clean$hnd_webcap %>% as.factor()
```


Service

Class Types and Structure
```{r}
glimpse(Service)
```
%NA
```{r}
sapply(Service, function(x) round((sum(is.na(x))/length(x)*100),3))
```

```{r}
summary(Service)
```
Extreme values
```{r}
plot(tele_clean$drop_data_Mean)
plot(tele_clean$blck_data_Mean)
plot(tele_clean$recv_sms_Mean)

#outlier_index <- which(tele_clean$drop_data_Mean > 100)
#tele_clean <- tele_clean[-outlier_index,]

#outlier_index <- which(tele_clean$blck_data_Mean > 300)
#tele_clean <- tele_clean[-outlier_index,]

#outlier_index <- which(tele_clean$recv_sms_Mean > 200)
#tele_clean <- tele_clean[-outlier_index,]
```

All clean of NA
```{r}
which(is.na(tele_clean))
```
Exporting for modelling.
```{r}
write_csv(tele_clean, "tele_clean.csv")
```